The Blue Obelisk five years on

### 2011-03-10 paper.tex
More on business

Developing a business model based on open source software generally relies on providing support, customisation and services around the software.

(Insert about eMolecules and Open Babel SMILES code...)

A recent example of such an interaction 
is Silicos, a Belgian company that provides services
in the area of cheminformatics, which has released several
command line applications based on Open Babel as well as donating code to the project. For example, the Pharao
tool released by them is a comprehensive solution for pharmacophore
searching that provides extensive support for a variety of
pharmacophore searches. Other tools released by them include Seive for
fitering by molecular property and XXX.

>>>>

Although the software developed by the Blue Obelisk is Open Source on principle, this does not rule out the establishment of a business based on open source chemistry software. Rather than supporting itself through sales, such a business generally relies on providing support, customisation and services around the software. The interaction between an open source project and a company is important, and works best where there is some form of ``giving back" to the project (such as developer time, code contributions, or finanical assistance with server costs).

An example of such an interaction was the donation by eMolecules, Inc. to Open Babel of code for the canonicalisation of molecules and fragments (Nov 2006). eMolecules is an online vendor of chemicals that uses Open Babel under-the-hood to manage its compound collections. Another more recent example occurred in July 2010 when Silicos, a Belgian company that provides services
in the area of cheminformatics, released several command line applications based on Open Babel as well as donating code to the project. For example, the Pharao
tool released by them is a comprehensive solution for pharmacophore
searching that provides extensive support for a variety of
pharmacophore searches. Other tools released by them include Seive for
fitering by molecular property and XXX.
